\hypertarget{postface}{%
\section*{Postface}\label{postface}}

\hypertarget{i-authors}{%
\subsection*{I. Authors}\label{i-authors}}

\begin{longtable}[]{@{}ll@{}}
\toprule
Name & Organisation\tabularnewline
\midrule
\endhead
Karin Bredenberg & National Archives of Sweden\tabularnewline
Luis Faria & Keep Solutions\tabularnewline
Miguel Ferreira & Keep Solutions\tabularnewline
Anders Bo Nielsen & Danish National Archives\tabularnewline
Jan Rörden & Austrian Institute of Technology\tabularnewline
Sven Schlarb & Austrian Institute of Technology\tabularnewline
Carl Wilson & Open Preservation Foundation\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{ii-revision-history}{%
\subsection*{II. Revision History}\label{ii-revision-history}}

\begin{longtable}[]{@{}llll@{}}
\toprule
Revision No. & Date & Authors(s) & Description\tabularnewline
\midrule
\endhead
0.1 & 20.09.2016 & Sven Schlarb & First draft based on E-ARK deliverable
D4.3.\tabularnewline
& & Jan Rörden &\tabularnewline
0.2 & 15.10.2016 & Miguel Ferreira & Comments,
Contribution\tabularnewline
& & Luis Faria &\tabularnewline
0.9 & 20.12.2016 & Sven Schlarb & Provided for internal
review\tabularnewline
& & & (E-ARK deliverable D4.4)\tabularnewline
0.9.1 & 06.01.2017 & Andrew Wilson & Comments and language
review\tabularnewline
0.9.2 & 13.01.2017 & Kuldar Aas & Comments\tabularnewline
1.0 & 27.01.2017 & Sven Schlarb & Address review comments and
language;\tabularnewline
& & Jan Rörden & final changes.\tabularnewline
2.0-DRAFT & 12.12.2018 & Sven Schlarb & Migration to markdown,
review\tabularnewline
& & Carl Wilson &\tabularnewline
2.0.0 & 15.05.2019 & Carl Wilson & Version 2.0.0\tabularnewline
& & Sven Schlarb &\tabularnewline
2.0.1 & 09.09.2019 & Carl Wilson & Site structure and PDF
layout\tabularnewline
2.0.4 & 12.06.2020 & K. Bredenberg & Preface text and output display
update\tabularnewline
& & C.Wilson &\tabularnewline
& & J. Kaminski &\tabularnewline
2.1.0 & 15.10.2021 & Sven Schlarb & Re-written to reflect the proposals
presented\tabularnewline
& & & in the White Paper published in Summer 2021.\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{iii-acknowledgements}{%
\subsection*{III Acknowledgements}\label{iii-acknowledgements}}

The E-ARK Archival Information Package (DIP) Specification was first
developed within the E-ARK project in 2014 -- 2017. E-ARK was an
EC-funded pilot action project in the Competitiveness and Innovation
Programme 2007- 2013, Grant Agreement no. 620998 under the Policy
Support Programme.

The authors of this specification would like to thank all national
archives, tool developers and other stakeholders who provided valuable
knowledge about their requirements for information packages and feedback
to this and previous versions of the specification.

\hypertarget{iv-contact--feedback}{%
\subsection*{IV Contact \& Feedback}\label{iv-contact--feedback}}

The E-ARK AIP specification is maintained by the Digital Information
LifeCycle Interoperability Standard Board (DILCIS Board). For further
information about the DILCIS Board or feedback on the current document
please consult the website
\href{http://www.dilcis.eu/}{http://www.dilcis.eu/} or
\href{https://github.com/dilcisboard}{https://github.com/dilcisboard} or
contact us at \href{mailto:info@dilcis.eu}{\nolinkurl{info@dilcis.eu}}.
